Initial Analysis

### 2019-08-20 Initial_Analysis.Rmd
Fixed double counting between same-nations eez issue (e.g. USA East coast and USA Gulf of Mexico)

@@

# Transboundary data
Spp <- list.files(Results_Path)
Results_Data <- GetTransResults(Spp)
head(Results_Data)
unique(Results_Data$Model_Index)
length(unique(Results_Data$TaxonKey)) #672 spp

@@

SubsetData <- TenTwenyfive %>% 
  filter(Name=="USA (East Coast)")

write.csv(SubsetData,
          "SubsetData.csv",
          row.names = F)

@@

sau_eez_fes <- read.csv("~/Desktop/sau_eez_fes.csv")

EEZID_D <- readxl::read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/Updated_EEZList_17June2016.xlsx")

# Trying to fix EEZ problem...

sau_eez_fes <-sau_eez_fes %>% 
rename(EEZID = eez_id)

eez_list <- EEZID_D %>% 
  rename(Country_Territory=Name)

xx <- Clean_Results %>% 
  left_join(eez_list,
            by = "Country_Territory") %>% 
  left_join(sau_eez_fes,
            by = "EEZID")

Neighbord_Territory_T <- Clean_Results %>% 
  group_by(Neighbor_Territory) %>% 
  summarise() %>% 
  left_join(eez_list_n,
            by = "Neighbor_Territory") %>% 
  left_join(sau_eez_fes,
            by = "EEZID") %>% 
  select(Neighbor_Territory,neighbor_entity = fishing_entity)

Non_duplicate_Data <- xx %>%   
  left_join(Neighbord_Territory_T,
              by ="Neighbor_Territory") %>% 
  mutate(
    fishing_entity = ifelse(is.na(fishing_entity),paste(Country_Territory),paste(fishing_entity)),
    Same_Nation = ifelse(fishing_entity==neighbor_entity,paste("Yes"),"No")
  ) %>% 
  filter(Same_Nation == "No")

write.csv(Non_duplicate_Data,
          "New_Clean_Results.csv")

@@

@@

```{Number_Tran_country, eval =F, echo =F}
# TI of 10% and MI > 50

>>>>

### Message for my brain

print("_____________________ WARNING DO NOT FORGET TO PULL/PUSH BEFORE YOU START_____________________")

@@

# Transboundary data
Spp <- list.files(Results_Path)
Results_Data <- GetTransResults(Spp)

head(Results_Data)
unique(Results_Data$Model_Index)
length(unique(Results_Data$TaxonKey)) #672 spp

@@

SubsetData <- Clean_Results %>% 
  filter(Country_Territory=="USA (East Coast)")

write.csv(SubsetData,
          "SubsetData.csv",
          row.names = F) # Using USA East coast and Gulf as example

@@

sau_eez_fes <- read.csv("~/GitHub/FishForVisa/Temporal_Data/sau_eez_fes.csv")

Neighbord_Territory_T <- Clean_Results %>% 
  group_by(eez_name=Neighbor_Territory) %>% 
  summarise() %>%
  left_join(sau_eez_fes,
            by = "eez_name") %>% 
  select(Neighbor_Territory= eez_name,
         NT_fishing_entity=fishing_entity
         )

Country_Territory_T <- Clean_Results %>% 
  group_by(eez_name=Country_Territory) %>% 
  summarise() %>%
  left_join(sau_eez_fes,
            by = "eez_name")  %>% 
  select(Country_Territory= eez_name,
         CT_fishing_entity=fishing_entity)

Non_duplicate_Data <- Clean_Results %>%   
  left_join(Neighbord_Territory_T,
              by ="Neighbor_Territory") %>% 
  left_join(Country_Territory_T,
              by ="Country_Territory") %>% 
  mutate(
    Same_Nation = ifelse(CT_fishing_entity==NT_fishing_entity,"Yes","No")
  ) %>% 
  filter(Same_Nation == "No")

# FIXED!!!!!

@@

- **Done debugging**

@@

```{Number_Tran_country, eval =F, echo =F}

# Clean out countries that share with their own borders

Neighbord_Territory_T <- Results_Data %>% 
  group_by(eez_name=Neighbor_Territory) %>% 
  summarise() %>%
  left_join(sau_eez_fes,
            by = "eez_name") %>% 
  select(Neighbor_Territory= eez_name,
         NT_fishing_entity=fishing_entity
         )

Country_Territory_T <- Results_Data %>% 
  group_by(eez_name=Country_Territory) %>% 
  summarise() %>%
  left_join(sau_eez_fes,
            by = "eez_name")  %>% 
  select(Country_Territory= eez_name,
         CT_fishing_entity=fishing_entity)

Clean_Results <- Results_Data %>%   
  left_join(Neighbord_Territory_T,
              by ="Neighbor_Territory") %>% 
  left_join(Country_Territory_T,
              by ="Country_Territory") %>% 
  mutate(
    Same_Nation = ifelse(CT_fishing_entity==NT_fishing_entity,"Yes","No")
  ) %>% 
  filter(Same_Nation == "No")

# TI of 10% and MI > 50
